Perfiles de Individualismo en la sociedad chilena

### 2025-08-16 paper.qmd
Actualiza sección de antecedentes

keywords: 
  - Individualismo
  - Individuación
  - Análisis de clases latentes
link-citations: true
linestretch: 1.15       
# mainfont: Times New Roman
# fontsize: 12pt          
geometry: "left=2.54cm,right=2.54cm,top=2.54cm,bottom=2.54cm"
papersize: letter
colorlinks: true
lang: es
bibliography: "tesis.bib"
---

@@

{{< include secciones/02-antecedentes.qmd >}}

{{< include secciones/03-metod.qmd >}}

@@

{{< include secciones/05-discusion.qmd >}}

{{< include secciones/06-conclusion.qmd >}}

>>>>

keywords: 
  - Individualismo
  - Individuación
  - Análisis de clases latentes
link-citations: true
linestretch: 1.15       
# mainfont: Times New Roman
# fontsize: 12pt          
geometry: "left=2.54cm,right=2.54cm,top=2.54cm,bottom=2.54cm"
papersize: letter
colorlinks: true
lang: es
bibliography: "input/bib/tesis.bib"
---

@@

<!-- {{< include secciones/02-antecedentes.qmd >}}

{{< include secciones/03-metod.qmd >}} -->

@@

<!-- {{< include secciones/05-discusion.qmd >}}

{{< include secciones/06-conclusion.qmd >}} -->
